On the marginal value of swimming in woodland caribou

### 2021-04-12 paper/manuscript.Rmd
fig1 caption
Fig2 caption

(ref:fig1) Photograph of swimming unmarked adult male caribou (*Rangifer tarandus*) from Western to Eastern Indian Island taken on 30 May 2017.

@@

(ref:fig2) A) Map of the Fogo Island archipelago with swimming events between islands. B) Histogram displaying the frequency of swimming events throughout the year. Note, colours correspond to individual caribou and vertical black bars delineate the ice-free season (April 1 to December 31). C) Inset of swimming events between small islands on the northern coast of Fogo island. D) Inset of swimming events between islands on the southern coast of Fogo island. Note, the grey diamond represents the location we observed an adult male caribou swimming (see Figure 1).

>>>>

(ref:fig1) Photograph of swimming unmarked adult male caribou (*Rangifer tarandus*) from Western 
Perry Island to Eastern Perry Island taken on 30 May 2017.

@@

(ref:fig2) A) Map of the Fogo Island archipelago with swimming events from 13 caribou between islands.
B) Correlation between area of an island (km2) and the residency in days an individual caribou spent
on that island (linear mixed effects regression with ID as a random effect: ß = 1.08, SE = 0.06; tdf =
177 = 17.5, p < 0.001). C) Inset of swimming events between small islands on the northern coast of
Fogo island. D) Inset of swimming events between islands on the southern coast of Fogo island. The
grey diamond represents the location we observed an adult male caribou swimming (see Figure 1). E)
Histogram displaying the frequency of swimming events throughout the year. Colors correspond to
individual caribou, which are consistent in all panels, and vertical black bars delineate the ice-free
season (April 1 to December 31).
